Think deep for reef resilience

### 2025-08-15 paper/paper_draft.qmd

Reefs in each timeseries cluster were compared to identify characteristics that differ
between low, medium and high coral cover clusters. These characteristics include reef median
depth, mean timeseries DHW, mean timeseries DHW tolerance level, Pearson’s correlation
between total coral cover and inversed DHW timeseries, proportion of coral habitable area
occupied by corals in the first timestep, ratio of source-to-sink larval connectivity and
total strength of all larval connections between reefs. To analyse the DHW tolerance levels
of reefs, heritable DHW tolerance values were tracked over timeseries in a matrix of shape
timestep \* taxa \* reef \* scenario matrix. The mean timeseries DHW tolerance was
calculated over the first four scenarios for each GCM (four from 4096 scenarios per GCM) due
to computational restraints, and then used to calculate an overall mean DHW tolerance value
for each reef under each GCM. **\[TI: Ben, is the last sentence here necessary?\]**

>>>>

Reefs in each timeseries cluster were compared to identify characteristics that differ
between low, medium and high coral cover clusters. These characteristics include reef median
depth, mean timeseries DHW, mean timeseries DHW tolerance level, Pearson’s correlation
between total coral cover and inversed DHW timeseries, proportion of coral habitable area
occupied by corals in the first timestep, ratio of source-to-sink larval connectivity and
total strength of all larval connections between reefs. To analyse the DHW tolerance levels
of reefs, heritable DHW tolerance values were tracked over timeseries in a matrix of shape
timestep \* taxa \* reef \* scenario matrix.
